Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-04-13 manuscript.tex
Manuscript accepted and online. [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/99586b8d0e1e0bcc787902b03e74230222f4995d.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/99586b8d0e1e0bcc787902b03e74230222f4995d/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/745401593

A published version of this manuscript is available at \url{https://doi.org/10.1186/s12903-021-01551-x}.
This current version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/6d0a6402c44cb9745875171d2d33c37b4d7fe4be...a58577793380052c7fdf515ff2a5360b9e525391}{has been updated} with minor corrections compared to the submitted version.
These errors have been corrected in the proof-stage at BMC Oral Health and are \emph{not} present in the published version.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/a58577793380052c7fdf515ff2a5360b9e525391/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/a58577793380052c7fdf515ff2a5360b9e525391}{habi/zmk-tooth-cohort-method-manuscript@a585777}
on April 13, 2021.

>>>>

A published version of this manuscript is available at \url{https://doi.org/10.1186/s12903-021-01551-x}.
The version of the manuscript you see here \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/6d0a6402c44cb9745875171d2d33c37b4d7fe4be...99586b8d0e1e0bcc787902b03e74230222f4995d}{has been updated} with minor corrections compared to the submitted version.
These errors have been corrected in the proof-stage at BMC Oral Health and are \emph{not} present in the published version.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/99586b8d0e1e0bcc787902b03e74230222f4995d/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/99586b8d0e1e0bcc787902b03e74230222f4995d}{habi/zmk-tooth-cohort-method-manuscript@99586b8}
on April 13, 2021.
